%-------------------------
% Resume in Latex
% Author : Aditya Nalge
% Based off of: https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tight margins for one-page fit
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands (Tight versions)
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\small$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

\begin{center}
    \textbf{\Huge \scshape ADITYA NALGE} \\ \vspace{2pt}
    \small 716-398-1735 $|$ \href{mailto:adinalge@gmail.com}{\underline{adinalge@gmail.com}} $|$ 
    \href{https://linkedin.com/in/adityanalge}{\underline{linkedin.com/in/adityanalge}} $|$
    \href{https://github.com/adityanalge}{\underline{github.com/adityanalge}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Palo Alto, CA}
      {Professional Program in Artificial Intelligence}{2024 -- Present}
    \resumeSubheading
      {SUNY Buffalo}{Buffalo, NY}
      {Master of Science in Computer Science and Engineering}{2016 -- 2018}
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology}{2012 -- 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deloitte}{2022 -- Present}
      {Software Engineer II}{San Jose, CA}
      \resumeProjectHeading{\textbf{Meta (Client)}}{}  
          \resumeItemListStart
            \resumeItem{Designed Hive and Data Swarm pipelines processing billions of rows for production analytics.}
            \resumeItem{Developed ML models to forecast resource demand and data center lifecycle costs.}
          \resumeItemListEnd
      \resumeProjectHeading{\textbf{Broadcom (Client)}}{}  
          \resumeItemListStart
            \resumeItem{Orchestrated zero-downtime global migration of Elastic logs to GCP and unified GitOps via Flux CD.}
            \resumeItem{Engineered HA Redis and Kubernetes migrations using Python and Terraform.}
          \resumeItemListEnd
      \resumeProjectHeading{\textbf{Cargill (Client)}}{}  
          \resumeItemListStart
            \resumeItem{Built an offline-first React Native app for 5,000+ assets with custom SAP data sync logic.}
            \resumeItem{Reduced API response times by 90\% by implementing Redux and async workflows.}
          \resumeItemListEnd

    \vspace{4pt} 
    \resumeSubheading
      {Marlabs}{2021 -- 2022}
      {Software Engineer}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Re-architected legacy LoopBack APIs to Express.js, reducing auth latency by 45\%.}
        \resumeItem{Designed a multi-tenant JWT system to securely onboard 10+ healthcare vendors.}
        \resumeItem{Led a zero-downtime production rollout of Login API V2 with integrated CI/CD.}
      \resumeItemListEnd

    \vspace{4pt} 
    \resumeSubheading
      {Nutanix}{2018 -- 2021}
      {Software Engineer}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Built an IaaS platform for one-click provisioning of 21-container environments via GKE.}
        \resumeItem{Developed a Full Stack management console using Node.js, TypeScript, and React.}
        \resumeItem{Engineered a Kafka-based audit microservice for high-performance data ingestion.}
        \resumeItem{Won 1st place at internal hackathon out of 274 teams for building a passwordless authentication system.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd % ONLY ONE END HERE

%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LLM Token Optimization \& Data Serialization Tool} $|$ \emph{Python, Tiktoken, TOON}}{2025}
          \resumeItemListStart
            \resumeItem{Engineered a TOON-based utility to minimize LLM context window usage for CSV, JSON, and YAML.}
            \resumeItem{Integrated tiktoken for real-time cost-reduction metrics during large-scale data ingestion.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Threshold Encryption System} $|$ \emph{Python, Cryptography, Shamir's Secret Sharing}}{2017}
          \resumeItemListStart
            \resumeItem{Built a cryptosystem using El Gamal and Shamir’s Secret Sharing for advanced data security.}
            \resumeItem{Engineered a multi-user threshold process to secure data via unique decryption shares.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \begin{tabular}{@{}p{0.9in} @{: } l}
      \textbf{Languages}  & Python, JavaScript, TypeScript, Node.js, SQL \\
      \textbf{Frameworks} & React, React Native, Express, Loopback4, Redux \\
      \textbf{Data/AI}    & TensorFlow, PyTorch, NumPy, Pandas, Scikit-learn, Data Swarm, Hive \\
      \textbf{DevOps}     & Kubernetes (CKA/CKAD), Docker, GKE, AWS, Terraform, Flux CD, Argo CD, Jenkins
     \end{tabular}
    }}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \begin{tabular}{@{}p{0.9in} @{: } l}
      \textbf{Kubernetes} & Certified Kubernetes Administrator (2023), Certified Kubernetes Application Developer (2020) \\
      \textbf{Specialized} & Certified Blockchain Expert (2018), Certified Ethical Hacker (2017)
     \end{tabular}
    }}
 \end{itemize}

\end{document}