%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (Reformatted for User)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape YOUR NAME} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:email@example.com}{\underline{email@example.com}} $|$ 
    \href{https://linkedin.com/in/yourprofile}{\underline{linkedin.com/in/yourprofile}} $|$
    \href{https://github.com/yourusername}{\underline{github.com/yourusername}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stanford University}{Palo Alto, CA}
      {Professional Program in Artificial Intelligence}{2026}
    \resumeSubheading
      {SUNY Buffalo}{Buffalo, NY}
      {Master of Science in Computer Science and Engineering}{2018}
    \resumeSubheading
      {University of Mumbai}{Mumbai, India}
      {Bachelor of Engineering in Information Technology}{2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deloitte}{Remote / On-site}
      {Software Engineer II}{2022 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Meta (Client):} Built and managed lifecycle dashboards for data center parts using 5 years of historical data; designed large-scale Hive/Data Swarm pipelines processing billions of rows for production-ready analytics.}
        \resumeItem{\textbf{Meta (Client):} Developed forecasting ML models to project demand and costs for future data center initiatives by synthesizing historical usage and resource performance data.}
        \resumeItem{\textbf{Broadcom (Client):} Orchestrated zero-downtime global migration of Elasticsearch/Kibana logs from Elastic Cloud to GCP across US, EU, and APAC regions.}
        \resumeItem{\textbf{Broadcom (Client):} Unified CI/CD workflows by transitioning GitOps pipelines from Argo CD to Flux CD, ensuring multi-cloud security compliance.}
        \resumeItem{\textbf{Cargill (Client):} Reduced API response times by 90\% (300s to 30s) by restructuring blocking logic into asynchronous Redux/SAP OData workflows.}
        \resumeItem{\textbf{Cargill (Client):} Architected an offline-first React Native application for 5,000+ industrial assets with custom sync logic to prevent data loss in low-connectivity environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Marlabs}{Piscataway, NJ}
      {Software Engineer}{2021 -- 2022}
      \resumeItemListStart
        \resumeItem{Re-architected legacy LoopBack 4 Login API to Express.js and Sequelize, reducing authentication latency by 45\%.}
        \resumeItem{Designed a multi-tenant JWT authentication system with isolated scopes, enabling secure onboarding for 10+ third-party healthcare vendors.}
        \resumeItem{Led zero-downtime production rollout of Login API V2 with full CI/CD integration and compliance adherence.}
      \resumeItemListEnd

    \resumeSubheading
      {Nutanix}{San Jose, CA}
      {Software Engineer}{2018 -- 2021}
      \resumeItemListStart
        \resumeItem{Built an IaaS platform automating one-click provisioning of 21-container environments across Docker, GKE, and Nutanix Kubernetes platforms.}
        \resumeItem{Developed a Full Stack management console using Node.js and React to automate digital certificate management.}
        \resumeItem{Engineered a distributed audit microservice using Kafka and MongoDB for high-performance data ingestion.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LLM Token Optimization \& Data Serialization Tool} $|$ \emph{Python, Tiktoken, TOON}}{Nov. 2025}
          \resumeItemListStart
            \resumeItem{Engineered a utility to minimize context window usage by converting CSV/JSON/YAML data into TOON format, reducing token consumption for large-scale ingestion.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Threshold Encryption System} $|$ \emph{El Gamal, Shamir’s Secret Sharing, Python}}{May 2017}
          \resumeItemListStart
            \resumeItem{Developed a multi-user decryption process requiring a threshold of authorized shares to unlock secure data.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages/Frameworks}{: Python, JS/TS, Node.js, React, React Native, SQL, Express, Redux, FastAPI} \\
     \textbf{Infrastructure/Cloud}{: Kubernetes (CKA/CKAD), Docker, Terraform, Flux CD, Argo CD, GKE, AWS, Jenkins} \\
     \textbf{Data/AI}{: TensorFlow, PyTorch, NumPy, Pandas, Scikit-learn, Data Swarm, Hive, Kafka, Redis, MongoDB}
    }}
 \end{itemize}

%-----------AWARDS & CERTIFICATIONS-----------
\section{Awards \& Certifications}
 \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Certified Kubernetes Administrator (CKA)} $|$ \emph{Cloud Native Computing Foundation}}{2023}
    \resumeProjectHeading
        {\textbf{1st Place Winner} $|$ \emph{Nutanix Hackathon 7.0 (Out of 274 Teams)}}{Feb. 2020}
    \resumeProjectHeading
        {\textbf{Certified Blockchain Expert / Ethical Hacker} $|$ \emph{Blockchain Council / EC-Council}}{2017 -- 2018}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
